Composable Generalized Consensus

### 2015-05-14 paper/paper.tex
A few changes

\section{Composable Generalized Consensus}
\label{sec:cgc}

@@

Command histories can be built from the empty history using the $\star$
operator, which appends a sequence of commands $cs$ to a history $h$, obtaining
the history $h \star cs$. We can then define define an ordering relation among
histories: $h_1 \leq h_2$ when there exists a sequence $cs$ such that $h_2 =
h_1 \star cs$. 
The maximum over a set of
histories $H$ is denoted by $Max\left( H \right)$ and $Max\left( \aset{}
\right)$ is the empty history.
Histories have the property that every finite set $H$ of 
histories has a \emph{greatest lower bound}, noted $GLB\left(H\right)$.
Finally, we say that a set of histories $H$ is compatible when all the histories in $H$ have a common upper bound $h$ such
that $h$ can be built using only commands found in the histories in $H$.

@@

@@

The next-state relation consists of three types of transitions:
$Crash\left( x \right)$ transitions; $Propose\left( l, c
\right)$ transitions, for a learner $l$ and a command $c$, in which
$c$ is inserted in the set $proposed$; $Learn\left( l,cs \right)$
transitions, for a learner $l$ and a sequence of commands $cs$, in
which $cs$ is inserted in $learned\left[ l \right]$. 
A $Learn\left( l, cs \right)$ transition is guarded by the following
conditions:
\begin{compactitem}
    \item[\textbf{Agreement}:] The set of learned histories after the transition, $\aset{learned'\left[ l
      \right] : l \in Learners}$, is compatible.
    \item[\textbf{Validity}:] Every learned sequence contains only
        proposed commands.  
    \item[\textbf{Irrevocability}:] The new learned sequence
        $cs$ is a strict extension of $Max\left(learned\left[ l
        \right]\right)$. 
        %\\ $cs > Max\left(learned\left[ l \right]\right)$.
\end{compactitem}

Thanks to the properties of Generalized Consensus, the clients, observing
their input commands and the received responses, see a
\emph{linearizable} execution
\cite{HerlihyWing90LinearizabilityCorrectnessConditionConcurrentObjects}.
Moreover, the service remains available as long as at least one
proposer and one learner are correct.

>>>>

\section{Generalized Consensus}
\label{sec:gc}

@@

Command histories can be built from the empty history using the $\star$
operator, which appends a sequence of commands $cs$ to a history $h$, obtaining
the history $h \star cs$. We can then define define an ordering relation among
histories: $h_1 \leq h_2$ when there exists a sequence $cs$ such that $h_2 = h_1
\star cs$. Histories have the property that every finite set $H$ of histories
has a \emph{greatest lower bound}, noted $GLB\left(H\right)$. Finally, we say
that a set of histories $H$ is compatible when all the histories in $H$ have a
common upper bound $h$ such that $h$ can be built using only commands found in
the histories in $H$.
%The maximum over a set of histories $H$ is denoted by $Max\left( H \right)$ and $Max\left( \aset{} \right)$ is the empty history.

@@

\subsection{Generalized Consensus}

@@

The next-state relation consists of three types of transitions:
$Crash\left( x \right)$ transitions; $Propose\left( l, c
\right)$ transitions, for a learner $l$ and a command $c$, in which
$c$ is inserted in the set $proposed$; $Learn\left( l,cs \right)$
transitions, for a learner $l$ and a sequence of commands $cs$, in
which $cs$ is inserted in $learned\left[ l \right]$. 
A $Learn\left( l, cs \right)$ transition is guarded by the following
conditions:
\begin{compactitem}
    \item[\textbf{Agreement}:] The set of learned histories after the transition, $\aset{learned'\left[ l
      \right] : l \in Learners}$, is compatible.
    \item[\textbf{Validity}:] Every learned sequence contains only
        proposed commands.  
    \item[\textbf{Irrevocability}:] The new learned sequence
        $cs$ is an extension of $learned\left[ l
        \right]$. 
        %\\ $cs > Max\left(learned\left[ l \right]\right)$.
\end{compactitem}

Thanks to the properties of Generalized Consensus, the clients, observing
their input commands and the received responses, see a
\emph{linearizable} execution
\cite{HerlihyWing90LinearizabilityCorrectnessConditionConcurrentObjects}.
